### 2020-07-16 code/figure1.Rmd
edits to figure 1-4. added function for fig4. adjusted table1 to show top largest n

fig1G <- ggplot(mut_order, aes(x = V1, y = log10mut, color = knn_clust)) + 
  geom_point() + 
  ylab("Log10(Mutation Count)") + 
  xlab("") +
  theme_classic() +
  facet_wrap(~ factor(knn_clust, levels = c(1:12)), ncol = 12, scales = "free_x") +
  geom_hline(data= mut_median, aes(yintercept=mut_med)) +
  scale_y_continuous(sec.axis = sec_axis(~.)) + ## dup y-axis
  scale_x_discrete(breaks = c(as.character(mut_order$V1[300]), as.character(xaxis_breaks$V1)), labels = c("n =" ,total_n$Freq)) +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks.x = element_blank(),
        axis.line.x = element_line(colour = "black", size = 0.5),
        axis.line.x.top = element_line(colour = "black", size = 0.5),
        #strip.background.x = element_blank(),
        strip.placement = "outside",
        strip.text.x = element_text(size = 12),
        legend.position = "none") +
  scale_color_manual(values = kelly.colours[-c(1:2)])

>>>>

fig1G <- ggplot(mut_order, aes(x = V1, y = log10mut, color = knn_clust)) + 
  geom_point() + 
  ylab("Log10(Mutation Count)") + 
  xlab("") +
  labs(tag = "G") +
  theme_classic() +
  facet_wrap(~ factor(knn_clust, levels = c(1:12)), ncol = 12, scales = "free_x") +
  geom_hline(data= mut_median, aes(yintercept=mut_med)) +
  scale_y_continuous(sec.axis = sec_axis(~.)) + ## dup y-axis
  scale_x_discrete(breaks = c(as.character(mut_order$V1[300]), as.character(xaxis_breaks$V1)), labels = c("n =" ,total_n$Freq)) +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks.x = element_blank(),
        axis.line.x = element_line(colour = "black", size = 0.5),
        axis.line.x.top = element_line(colour = "black", size = 0.5),
        #strip.background.x = element_blank(),
        strip.placement = "outside",
        strip.text.x = element_text(size = 12),
        legend.position = "none") +
  scale_color_manual(values = kelly.colours[-c(1:2)])

### 2020-07-16 code/figure3.Rmd
edits to figure 1-4. added function for fig4. adjusted table1 to show top largest n

```{r group-pathway-enrichment heatmap, fig.cap="**Figure 3. Pathway-specific enrichment within clusters.** Heatmap shows relative enrichment of each pathway (rows) within each numbered cluster (columns). The annotation at left indicates the Reactome pathway group at the second level (check this)."}
load("../data/effect_heatmap.Rda") ## load data

effect_colors = c("1" = "#2d004b", "2" = "#542788", "3" = "#8073ac", "4" = "#b2abd2", "5" = "#d8daeb", "6" = "white", "7" = "#fee0b6", "8" = "#fdb863", "9" = "#e08214","10" = "#b35806","11" ="#7f3b08") ## color scheme

fig3 <- ggplot(data = effect_heatmap, aes(x=cluster, y=path_name)) + 
  geom_tile(size = 0.6, aes(fill = discrete_color)) +
  scale_fill_manual(values = effect_colors) +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "none")

fig3_legend <- ggplot(data = data.frame(x = 1:11, y = 1), aes(x = x, y = y, fill = as.factor(x))) +
  geom_bar(stat = "identity", width = 1) +
  theme_classic() +
  scale_fill_manual(values = effect_colors) + 
  scale_x_continuous(labels= c("-1", "-0.5","0", "0.5", "1")) +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.line = element_blank())

## setting patchwork panel layout
layout <- '
AAAAA
AAAAA
AAAAA
AAAAA
AAAAA
AAAAA
AAAAA
AAAAA
#BBB#
'

fig3 + fig3_legend + plot_layout(design = layout)
```

>>>>

```{r group-pathway-enrichment heatmap, fig.width= 5, fig.height= 10, fig.align= 'center', fig.cap="**Figure 3. Pathway-specific enrichment within clusters.** Heatmap shows relative enrichment of each pathway (rows) within each numbered cluster (columns). The annotation at left indicates the Reactome pathway group at the second level (check this)."}
load("../data/effect_heatmap.Rda") ## load data
effect_heatmap$test <- 1
class(effect_heatmap$cluster)
effect_colors = c("1" = "#2d004b", "2" = "#542788", "3" = "#8073ac", "4" = "#b2abd2", "5" = "#d8daeb", "6" = "white", "7" = "#fee0b6", "8" = "#fdb863", "9" = "#e08214","10" = "#b35806","11" ="#7f3b08") ## color scheme

fig3 <- ggplot(data = effect_heatmap, aes(x=cluster, y=path_name)) + 
  geom_tile(size = 0.6, aes(fill = discrete_color)) +
  scale_fill_manual(values = effect_colors) +
  ylab("377 Reactome Pathways") +
  xlab("Cluster") +
  theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "none")
fig3_legend <- ggplot(data = data.frame(x = 1:11, y = 1), aes(x = x, y = y, fill = as.factor(x))) +
  geom_bar(stat = "identity", width = 1) +
  theme_classic() +
  scale_fill_manual(values = effect_colors) + 
  scale_x_continuous(labels= c("-1", "-0.5","0", "0.5", "1")) +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.line = element_blank())

# ## setting patchwork panel layout
# layout <- '
# AAAAA
# AAAAA
# AAAAA
# AAAAA
# AAAAA
# AAAAA
# AAAAA
# AAAAA
# AAAAA
# AAAAA
# AAAAA
# AAAAA
# #BBB#
# '
# 
# fig3 + fig3_legend + plot_layout(design = layout)

fig3_legend <- plot_grid(NULL, fig3_legend, NULL, ncol = 3)

plot_grid(fig3, fig3_legend, ncol = 1, rel_heights = c(15, 1))
```
